Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2022-04-01 doc/AMS-15/AMS-15_paper/AMS-15_paper.Rmd
Add information on core samples

@@

A suite of 15 carbonate macrofossils consisting of shell and coral fragments from a series of coastal marine cores REF were measured as graphite and as CO~2~ using the HGIS method to further test the method and serve to demonstrate a potential application. coral macrofossils from a subtropical coastal marine sediment core using our gas method and compared to the same samples measured using the traditional graphite method.

To further test the method and a potential application, we measured 15 shell and coral macrofossils from a subtropical coastal marine sediment core using our gas method and compared to the same samples measured using the traditional graphite method.

@@

>>>>

Reference and process blank materials were not pretreated or cleaned. Carbonate shell samples for the core comparison study were picked from a split core and cleaned by washing with distilled water and dried at 60 C. Shell samples were crushed and mixed, but not otherwise pretreated. Other? Sonication?

@@

A suite of 15 carbonate macrofossils consisting of shell and coral fragments from a series of coastal marine cores @moser2021 were measured as graphite and as CO~2~ using the HGIS method to further test the method and serve to demonstrate a potential application. Sediment cores were collected from Baie des Baradères, Haiti during a scientific cruise in May 2016 lead by Dr. Jeffrey Donnelly (WHOI). Coring was performed with a Rossfelder vibracorer from a 20-foot pontoon boat. The cores were collected from a coastal karst basin (CKB) at vertical depth \~11.7 m and coordinates 18.514° N, 73.629° W. Core HATC1 D1 is 145 cm long and was collected in a 3-inch poly tube as a control directly beside core HATC1 D2, which is a continuous 896 cm core collected in a 3-inch aluminum tube. Carbonate materials such as corals and bivalve shells were selected throughout the core for the age-depth model.

age range

@@

We applied a correction for the regional marine reservoir effect with a delta R of -216 and uncertainty 92 based on the oxcal model with 10 reservoir points. Samples with radiocarbon age \> 0 were calibrated using the Marine20 curve @heaton_marine20marine_2020. The NH1 curve from Hua et. al @hua_atmospheric_2013 was used for calibration of postmodern dates.
